---
title: "Cambridge CC Fastest Times"
date: today
date-format: "YYYY"
author: "Simon Bond"
format: gfm
prefer-html: true
---

# Purpose

This is the output from an automated check of results on <https://www.cyclingtimetrials.org.uk/find-results>. This happens once a week in the early hours of a monday.  It goes back one week earlier than the previous check's last date, and then trawls through the new ones to pick up results from members of Cambridge CC. 

An annual prize is awarded to the fastest time that year for several distances. Checking by hand is time consuming, so I wrote this code. 

# Results


```{r process}
#| echo: false
#| message: false
#| warning: false

library(tidyverse)
library(kableExtra)
load( "all_times.rds")

top_five <- all_times %>% 
  mutate( hrs = str_split_i(Time,":",1) %>% as.numeric,
          mins =str_split_i(Time,":",2)%>% as.numeric,
          sec =str_split_i(Time,":",3)%>% as.numeric
          ) %>% 
  arrange(distance, hrs, mins, sec) %>% 
  group_by(distance) %>% 
  slice_head(n=5) %>% 
  select(distance, Time, `First Name`, `Last Name`,Position,url) %>% 
  as.data.frame 
top_five %>% 
  kbl() %>% 
  kable_styling() %>% 
  column_spec(6, link=top_five$url)

Sys.setenv(TZ="Europe/London")
yr <- Sys.Date() %>% as.Date %>% year()
```

This document was generated on `r Sys.time()` .


# Data

The complete set of data for Cambridge CC riders is 
```{r, echo=FALSE, results='asis'}
filename <- paste0("tt_result_scraping.wiki/all_results_",yr,".csv")
cat(paste0('<a href="all_results_',yr,'.csv" download="all_results_',yr,'.csv"> here </a>'))
```


